---
title: "Geography 176A"
author: "[Leslie Alonzo](https://LeslieAlonzo98.github.io)"
subtitle: 'Daily Exercise 15'
output:
  html_document:
    theme: journal
---

```{r Import libraries,include=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(sf)
library(stars)
library(units)
library(raster)
library(mapview)
library(leaflet)
library(gdalUtilities)
library(rmapshaper)
library(knitr)
library(kableExtra)
library(readxl)
```

```{r Functions, include=FALSE, message=FALSE, echo=FALSE}
get_conus = function(data, var){
  conus = filter(data, !get(var) %in% c("Hawaii", "Puerto Rico", "Alaska", "Guam", "District of Columbia"))
  return(conus)
}

plot_tess = function(data, title){
  ggplot() + 
    geom_sf(data = data, col = "white", size = .2) +   
    theme_void() +
    theme(legend.position = 'none',
          plot.title = element_text(face = "bold", color = "darkblue", hjust = .5, size = 24)) +
    labs(title = paste0(title),
         caption = paste0(nrow(data), " features"))
}

plot_pip = function(data){
  ggplot() +
    geom_sf(data = data, aes(fill = log(n)), alpha = .9, size = .2) +
    scale_fill_gradient(low = "white", high = "darkgreen") +
    theme_void() +
    theme(legend.position = 'none',
          plot.title = element_text(face = "bold", color = "darkgreen", hjust = .5, size = 24)) +
    labs(title = "Counties in Each State",
         caption = paste0(sum(data$n), " Counties represented"))
}

point_in_polygon3 = function(points, polygon, group){
  st_join(polygon, points) %>%
    st_drop_geometry() %>%
    count(get(group)) %>%
    setNames(c(group, "n")) %>%
    left_join(polygon, by = group) %>%
    st_as_sf()
}

step2function = function(data, string){
  
  newframe = data %>% 
    mutate(area = st_area(data)) %>% 
    drop_units() %>% 
    mutate(area = area*0.000001)
  dataframe = data.frame(type = string,
                num_feat = nrow(newframe),
                mean_area = mean(newframe$area),
                st_dev = sd(newframe$area),
                tot_area = sum(newframe$area))
 
  return(dataframe)
}

```

```{r Question 1, include=FALSE, message=FALSE, echo=FALSE}
#Question 1

conus = USAboundaries::us_states() %>%
  st_as_sf(coords = c("lng", "lat"), crs = 4326)

counties2 = get_conus(USAboundaries::us_counties(), "state_name") %>%
  st_transform(st_crs(conus)) %>%
  dplyr::select(name)

counties = get_conus(USAboundaries::us_counties(), "state_name") %>%
  st_transform(st_crs(conus)) %>%
  dplyr::select(geoid)

polygon = get_conus(conus, "name") %>%
  dplyr::select(name)

join1 = st_join(polygon, counties) %>%
  st_drop_geometry() %>%
  count(name) %>%
  left_join(polygon, by = 'name') %>%
  st_as_sf()



pip_counties = point_in_polygon3(join1, counties, "geoid") %>% 
  dplyr::select(n)



plot_pip(pip_counties)




pip_counties = st_transform(pip_counties, 5070)

pip_cent = st_centroid(pip_counties)

ggplot() +
  geom_sf(data = pip_counties) +
  geom_sf(data = pip_cent) +
  theme_gray()



plot_tess(pip_counties, "Original")

countyarea = step2function(pip_counties, "Original")

#cOVERAGE SQUARE GRID

pip_counties_grid = st_make_grid(pip_counties, n = c(70, 50)) %>% 
  st_as_sf() %>% 
  mutate(id = 1:n())

plot_tess(pip_counties_grid, "Square Grid")

squarearea = step2function(pip_counties_grid, "Square Grid")

#COVERAGE HEX GRID

pip_counties_hexgrid = st_make_grid(pip_counties, n = c(70, 50), square = FALSE) %>% 
  st_as_sf() %>% 
  mutate(id = 1:n())

plot_tess(pip_counties_hexgrid, "Hexagon Grid")

hexagonarea = step2function(pip_counties_hexgrid, "Hexagon Grid")

# VORONI TESSELLATION

pip_counties_u = st_union(pip_cent)

v_grid = st_voronoi(pip_counties_u) %>% 
  st_cast() %>% 
  st_as_sf() %>% 
  mutate(id = 1:n())

v_grid_final = st_intersection(v_grid, st_union(pip_counties))

plot_tess(v_grid_final, "Voroni Coverage") + 
  geom_sf(data = pip_counties_u, col = "darkred", size = .2)

voroniarea = step2function(v_grid_final, "Voroni Coverage")

#TRIANGULATED TESSELLATION

t_grid = st_triangulate(pip_counties_u) %>% 
  st_cast() %>% 
  st_as_sf() %>% 
  mutate(id = 1:n())
         
t_grid_final = st_intersection(t_grid, st_union(pip_counties))

plot_tess(t_grid_final, "Triangulated Coverage") + 
  geom_sf(data = pip_cent, col = "darkred", size = .3)

triangulatedarea = step2function(t_grid_final, "Triangulated Coverage")
```

```{r plots, message=FALSE}
plot_tess(pip_counties, "Original")

plot_tess(pip_counties_grid, "Square Grid")

plot_tess(pip_counties_hexgrid, "Hexagon Grid")

plot_tess(v_grid_final, "Voroni Coverage") + 
  geom_sf(data = pip_counties_u, col = "darkred", size = .2)

plot_tess(t_grid_final, "Triangulated Coverage") + 
  geom_sf(data = pip_cent, col = "darkred", size = .3)

```

```{r Question 2, include=FALSE, message=FALSE, echo=FALSE}
tess_summary = bind_rows(countyarea, squarearea, hexagonarea, triangulatedarea, voroniarea)
  

knitr::kable(tess_summary,
             col.names = c("Type", "Number of Features", "Mean Area", "St. Dev", "Total Area"),
             caption = "Summary of Our 5 Tesselations")%>% 
  kableExtra::kable_styling("striped", full_width = TRUE, font_size = 10) 

```

```{r}
knitr::kable(tess_summary,
             col.names = c("Type", "Number of Features", "Mean Area", "St. Dev", "Total Area"),
             caption = "Summary of Our 5 Tesselations")%>% 
  kableExtra::kable_styling("striped", full_width = TRUE, font_size = 10) 
```

Differences in each tesselation 

-Original: Visually, it is represented the best. The downfall is that it differs the most in standard deviation, which doesn't help when trying to do something with equal area.

-Square/Hexagon: These tesselations have the least standard deviation and because they are displayed to be equally represented, it results in the least amount of features. 

-Voronoi: This tesselation has the greatest variance in the sizes, but is the closest to the original tesselation

-Triangulation: This tesselation provides twice as much features which improves it accuracy, but process slower.

